Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-26 EconGrowth.Rnw
Now generating data graphs for all countries.

createCountryInputGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graph <- xyplot(iGDP+iQ+iX+iU ~ iYear, data=dataTable,
                  type="l",
                  scales=list(cex=1.5, tck=-1),
                  ylab="Indexed (1980=1)",
                  auto.key=list(columns=1))
  return(graph)
}

createCountryInputGraph("US")

>>>>

createCountryInputGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graph <- xyplot(iGDP+iQ+iX+iCapStk+iLabor ~ iYear, data=dataTable,
                  type="l",
                  scales=list(cex=1.0, tck=-0.5),
                  ylab="Indexed (1980=1)",
                  auto.key=list(columns=1, x=0.0, y=0.98))
  return(graph)
}

createCountryInputGraph("US")
lapply(countries, createCountryInputGraph)
